CLT Gafo merge

### 2022-04-20 analysis/clt_gafo_merge.Rmd
prep item selection

```{r}
ggarrange(
  ggplot(merge, aes(x = time_diff))+
  geom_histogram(alpha = .75, col = "black", fill = "white", bins = 100)+
  labs(x = "Time (in years) between tests", y = "Count")+
  scale_color_viridis_c(name = "Age")+
  #ylim(0.7,1)+
  #coord_fixed(3)+
  theme_minimal(),

>>>>

```{r}
ggarrange(
  # ggplot(merge, aes(x = time_diff))+
  # geom_histogram(alpha = .75, col = "black", fill = "white", bins = 100)+
  # labs(x = "Time (in years) between tests", y = "Count")+
  # scale_color_viridis_c(name = "Age")+
  # #ylim(0.7,1)+
  # #coord_fixed(3)+
  # theme_minimal(),
